### 2020-09-03 text/manuscript.tex
Add Zenodo DOI
Fix typos

% Title must be 250 characters or less.
\begin{flushleft}
{\Large
\textbf\newline{Business disruptions from social distancing} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
Miklós Koren\textsuperscript{1,2,3\Yinyang\textcurrency*},
Rita Pető\textsuperscript{2\ddag}
\\
\bigskip
\textbf{1} Central European University, Budapest, Hungary
\\
\textbf{2} KRTK KTI, Budapest, Hungary
\\
\textbf{3} CEPR, London, UK
\\
\bigskip

@@

\section*{Data Availability Statement}
The mobility data used in thirds paper \cite{SafeGraph2020-gn} is proprietary, but may be obtained free of charge for COVID-19-related research from the COVID-19 Consortium. The authors are not affiliated with this consortium. Researchers interested in access to the data can apply at \url{https://www.safegraph.com/covid-19-data-consortium} (data manager: Ross Epstein, ross@safegraph.com). After signing a Data Agreement, access is granted within a few days. The Consortium does not require coauthorship and does not review or approve research results before publication. Datafiles used: \texttt{/monthly-patterns /patterns\_backfill/2020/05/07/12/2020/02/ patterns-part[1-4].csv.gz} (Monthly Places Patterns for February 2020, released May 7, 2020), \texttt{/monthly-patterns/patterns/2020/06/05/06/patterns-part[1-4].csv.gz} (Monthly Places Patterns for February 2020, released June 5, 2020) and \texttt{/core/2020 /06/Core-USA-June2020-Release-CORE\_POI-2020\_05-2020-06-06.zip} (Core Places for June 2020, released June 6, 2020). The COVID-19 Consortium will keep these datafiles accessible for researchers. The authors will assist with any reasonable replication attempts for two years following publication.

The code and all other data underlying our analysis are licensed for public use and will be made available on Zenodo.

>>>>

% Title must be 250 characters or less.
\begin{flushleft}
{\Large
\textbf\newline{Business disruptions from social distancing} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
Miklós Koren\textsuperscript{1,2,3\Yinyang\textcurrency*},
Rita Pető\textsuperscript{2\ddag}
\\
\bigskip
\textbf{1} Central European University, Budapest, Hungary
\\
\textbf{2} Centre for Economic and Regional Studies, Budapest, Hungary
\\
\textbf{3} CEPR, London, United Kingdom
\\
\bigskip

@@

\section*{Data Availability Statement}
The mobility data used in this paper \cite{SafeGraph2020-gn} is proprietary, but may be obtained free of charge for COVID-19-related research from the COVID-19 Consortium. The authors are not affiliated with this consortium. Researchers interested in access to the data can apply at \url{https://www.safegraph.com/covid-19-data-consortium} (data manager: Ross Epstein, ross@safegraph.com). After signing a Data Agreement, access is granted within a few days. The Consortium does not require coauthorship and does not review or approve research results before publication. Datafiles used: \texttt{/monthly-patterns /patterns\_backfill/2020/05/07/12/2020/02/ patterns-part[1-4].csv.gz} (Monthly Places Patterns for February 2020, released May 7, 2020), \texttt{/monthly-patterns/patterns/2020/06/05/06/patterns-part[1-4].csv.gz} (Monthly Places Patterns for February 2020, released June 5, 2020) and \texttt{/core/2020 /06/Core-USA-June2020-Release-CORE\_POI-2020\_05-2020-06-06.zip} (Core Places for June 2020, released June 6, 2020). The COVID-19 Consortium will keep these datafiles accessible for researchers. The authors will assist with any reasonable replication attempts for two years following publication.

The code and all other data underlying our analysis are licensed for public use and are available on Zenodo at \url{http://doi.org/10.5281/zenodo.4013502}.
